DOpElib:\\ Differential Equations and Optimization Environment

### 2022-07-11 Examples/PDE/StatPDE/Example12/content.tex
Ueberarbeitung PDE Statpde examples mit Ausnahme von 9 und 10.
Added Benchmark fracture examples - and spellcheck in content files
Now the spacetimehandlers utilize the userprovided component-block mapping also in the renumbering of the dofs

\subsubsection{General problem description}
This example shows the use of the Raviart-Thomas (RT) element in \texttt{DOpElib}. The example 
is taken from \texttt{dealii} step-20 and shows how this step can be implemented in \texttt{DOpElib}.

Most things are identical to all the other programs. However there is a subtle difference in 
\texttt{localpde.h}: Although the element used has 3 components (two for the RT-Element and 1 for the pressure)
the block\underline{ }component vector mapping blocks to components has only 2 entries. 1 for each finite element used!

>>>>

\subsubsection{General problem description}
This example shows the use of the Raviart-Thomas (RT) element in \texttt{DOpElib}. The example 
is taken from \texttt{dealii} step-20 and shows how this step can be implemented in \texttt{DOpElib}. The vector valued Laplace equation is solved in the mixed formulation.

Most things are identical to all the other programs. However there is a subtle difference in 
\texttt{localpde.h}: The block\underline{ }component vector mapping
blocks to components has 3 entries, but since the first finite element
is non-primitive we need to assign both components (0 and 1) to the
same block.
